\subsection{Thesis Overview}
This thesis seeks to answer the research questions outlined above through
the presentation of eight chapters. This first chapter serves as an
introduction to the rest of the work, including a brief background section
that defining major concepts.
Chapter \ref{ch/intro} provides a more in-depth presentation of concepts
covered by way of literature review.
The next four chapters,
Chapters \ref{ch/xray} - \ref{ch/sf}, are published or intend to be
published. Chapter \ref{ch/xray} is based on work published in the
Journal of The Minerals, Metals and Materials Society. This chapter
explores the feasibility of comparing analyses of x-radiography
images to compositional mapping of the same sample.
Chapters \ref{ch/melt} - \ref{ch/sf} are each separate manuscripts
intended for publication. Chapter \ref{ch/melt} describes analyses
procedures developed to calculate solidification velocities procedurally
for two separate solidification experiments. The results of each procedure
are compared to manual measurements.
Chapter \ref{ch/seg} presents a new procedure for segmenting irregular and
tightly-packed particles, extended from current procedures commonly
referred to in literature.
Chapter \ref{ch/sf} presents a software package developed to establish
a segmentation workflow and create geometries to be used in image-based
physics modeling.
Chapter \ref{ch/summary} summarizes the work across the chapters and
provides some conclusions.
Finally, Chapter \ref{ch/future} provides recommendations for future
work following the work covered in this thesis.

